|

### 2021-12-24 paper/dcpo_demsupport.Rmd
fuss with abstract

abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. Such approaches come with concomitant measurement uncertainty that should be taken into account, however, and neither study incorporated this uncertainty into its analyses. Correcting this oversight reveals that there is no support for either study's conclusion. Efforts to minimize the uncertainty by incorporating additional survey data still fail to yield evidence in support of either hypothesis. These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and of accounting for measurement uncertainty when working with latent variables. [150/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."

>>>>

abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. Such approaches come with concomitant measurement uncertainty that should be taken into account, however, and neither study incorporated this uncertainty into its analyses. Correcting this oversight reveals that there is no support for either study's conclusion. Efforts to minimize the uncertainty by incorporating additional data still fail to yield evidence in support of either hypothesis. These results underscore the need both for more nuanced analyses of the relationships between public support and democracy and for taking measurement uncertainty into account when working with latent variables. [150/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables."
